PANCHANGE_data_preprocessing

### 2020-08-05 PANCHANGE_data_preprocessing2020-07-15.Rmd
edited and finalised COVID algorithm

++KT: Needs to be developed further for RAMP dataset
COVID prediction model for COPING
```{r eval=FALSE, include=FALSE}
# Formula to calculate probability 
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

# Calcualte the odds ratios 
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_odds_ratio = 
		      exp(covid_probability) / (1 + exp(covid_probability))

# generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column)
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
		      )

@@

## creating a frequency table. Previous code: table covid_odds_ratio_50, c(min covid_odds_ratio max covid_odds_ratio)
covid_variables <- c(
                      "covid_odds_ratio_50",
                      "covid_odds_ratio",
                      "covid_probability"
                    )

>>>>

++KT: Needs to be developed further for RAMP dataset
COVID prediction model for COPING

```{r create numeric sex variable with male=1}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    Sex_respiratory =
      if_else(
        Sex == "Male",
        1,
        0
      )
  )
```

```{r how many people expereinced all symptoms}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    people_with_symptoms =
      if_else(
          !is.na(respiratory.anosmia_binary) &
          !is.na(respiratory.pcough_binary) &
          !is.na(respiratory.fatigue_binary) &
          !is.na(respiratory.skipped_meals_binary),
        1,
        0
       )
  )

table(dat.glad.coping$people_with_symptoms)
```

```{r COVID prediction model}
# linear model of covid symptoms
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex_respiratory) + 
		      (1.75*respiratory.anosmia_binary) + 
		      (0.31*respiratory.pcough_binary) +  
		      (0.49*respiratory.fatigue_binary) +  
		      (0.39*respiratory.skipped_meals_binary) 
		         )

# Calcualte the odds ratios 
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    covid_odds_ratio = 
      (exp(covid_probability) / (1 + exp(covid_probability)))
  )

# generate binary cutt off variable for risk of COVID 
dat.glad.coping <- dat.glad.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
		      )
		  )

@@

#frequency table for covid variables 
covid_variables <- c("covid_odds_ratio",
                      "covid_probability"
                    )
